---
title: "Rmd_for_Exam4(exam_3_redo)"
author: "Steven Smith"
date: "4/27/2021"
output: html_document
---

```{r,echo=FALSE,message=FALSE,warning=FALSE}
library(janitor)
library(patchwork)
library(tidyverse)
library(readxl)
library(tidyr)
library(ggplot2)
library(MASS)
library(skimr)
library(broom)
library(GGally)
library(modelr)
library(fitdistrplus)
library(plotly)
library(dplyr)

```

<style type="text/css">
.main-container {
  max-width:1800px;
  margin-left: auto;
  margin-right; auto;
}
</style>

<style>
div.orange { background-color:#ab6238; border-radius: Spx; padding: 20px;}
</style>
<div class = "orange">

### Faculty Salaries
#### Re-creating graph 1

```{r,echo=FALSE,message=FALSE,warning=FALSE}
df1 <- read.csv("./FacultySalaries_1995.csv")

df1b <- df1 %>% 
  select(FedID, UnivName, State, Tier, contains("Salary")) %>% 
  select(-contains("All")) %>% 
  pivot_longer(starts_with("Avg"),names_to = "Rank", values_to = "Salary") %>% 
  mutate(Rank = Rank %>% str_remove_all("Avg")) %>% 
  mutate(Rank = Rank %>% str_remove_all("ProfSalary")) %>% 
  filter(Tier != "VIIB") 

  ggplot(df1b,aes(x=Rank,y=Salary,fill=Rank)) +
  geom_boxplot() +
  facet_wrap(~Tier) +
  theme_minimal() +
  theme(axis.text.x=element_text(angle =60,hjust = 1 ))
mod1a <- aov(data = df1b,
             formula = Salary ~ State + Tier + Rank)

summary(mod1a)
```

##### ANOVA model testing the influence of "State", "Tier", and 
"Rank" on "Salary" and not including any interactions between those predictors.

___

### Juniper Data
#### Re-creating graph 2

```{r,echo=FALSE,message=FALSE,warning=FALSE}

df2 <- read.csv("./Juniper_Oils.csv")

names(df2) <- names(df2) %>% make_clean_names()


df2 <- df2 %>% 
  pivot_longer(cols=c("alpha_pinene","para_cymene","alpha_terpineol",
                      "cedr_9_ene","alpha_cedrene","beta_cedrene","cis_thujopsene",
                      "alpha_himachalene","beta_chamigrene","cuparene","compound_1",
                      "alpha_chamigrene","widdrol","cedrol","beta_acorenol","alpha_acorenol",
                      "gamma_eudesmol","beta_eudesmol","alpha_eudesmol","cedr_8_en_13_ol",
                      "cedr_8_en_15_ol","compound_2","thujopsenal"),
               names_to="compounds",
               values_to="mass_spec_OD")

ggplot(df2,aes(x=years_since_burn, y=mass_spec_OD)) +
  geom_point(alpha=.001) + facet_wrap(~compounds,scales = "free_y") + geom_smooth() + 
  theme_minimal() +
  labs(x="YearsSinceBurn",y="Concentration")


mod2a <- glm(data = df2,
            formula = mass_spec_OD ~ years_since_burn * compounds)

tidy(mod2a) %>% 
  filter(p.value<0.05)
```
Used a generalized linear model to find which chemicals show concentrations that are significantly affected by "Years Since Burn".